---
title: "HW3"
author: "Tongxi Yu"
date: "2023-10-12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1

How many aisles are there, and which aisles are the most items ordered from?
Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
library(p8105.datasets)
library(dplyr)
library(ggplot2)
data("instacart")
instacart = 
  instacart |> 
  as_tibble()
```
## How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart |> 
  count(aisle) |> 
  arrange(desc(n))
tail(names(sort(table(instacart$aisle_id))),1)
```
There are 134 aisles are there. Aisle 83 are the most items ordered from.

## Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart |> 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) |>
  group_by(aisle) |> 
  count(product_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  knitr::kable()
```

# Question 2

```{r}
library(p8105.datasets)
data("brfss_smart2010")
```


## Data Cleaning

```{r}
brfss_smart2010 = brfss_smart2010 |>
  janitor::clean_names()

overall_health = brfss_smart2010 |>
  filter(topic == "Overall Health") |>
  filter(response %in% c("Poor", "Fair", "Good", "Very Good", "Excellent")) |>
  arrange(desc(response))
```

## In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
#2002 data
data2002 = overall_health |>
  filter(year == "2002") 

stateOver7_2002 <- data2002 |>
  group_by(locationabbr) |>
  summarise(locations_observed = n_distinct(locationdesc)) |>
  filter(locations_observed >= 7)
stateOver7_2002$locationabbr
#2010 data
data2010 = overall_health |>
  filter(year == "2010") 

stateOver7_2010 <- data2010 |>
  group_by(locationabbr) |>
  summarise(locations_observed = n_distinct(locationdesc)) |>
  filter(locations_observed >= 7)
stateOver7_2010$locationabbr
```
"CT" "FL" "MA" "NC" "NJ" "PA" were observed at 7 or more locations in 2002
"CA" "CO" "FL" "MA" "MD" "NC" "NE" "NJ" "NY" "OH" "PA" "SC" "TX" "WA" were observed at 7 ore more locations in 2010.

# Make a “spaghetti” plot of this average value over time within a state 

```{r}
excellent_data <- overall_health |>
  filter(response == "Excellent")

grouped_data <- excellent_data |>
  group_by(year, locationabbr) |>
  summarise(average_data_value = mean(data_value))

# 3. Create a "spaghetti" plot
ggplot(grouped_data, aes(x = year, y = average_data_value, group = locationabbr, color = locationabbr)) +
  geom_line() +
  labs(x = "Year", y = "Average Data Value", title = "Average Data Value Over Time by State (Excellent Responses)") +
  theme_minimal()
```
# Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State

```{r}
subset_data <- overall_health |>
  filter(year %in% c(2006, 2010),locationabbr == "NY")

# Create a two-panel plot
ggplot(subset_data, aes(x = data_value, fill = response)) +
  geom_histogram(binwidth = 1, color = "black") +
  facet_grid(year ~ .) +
  labs(x = "Data Value", y = "Frequency", title = "Distribution of Data Value in NY State (In 2006 and 2010)") +
  scale_fill_manual(values = c("Poor" = "red", "Fair" = "orange", "Good" = "yellow", "Very Good" = "green", "Excellent" = "blue")) +
  theme_minimal()
```

